Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-05-29 pirouette_supplement.tex
Use '\newpage' instead of '\clearpage' as the latter destroys the layout and adds a lot of comma's for some reason :confused:

\clearpage
%\newpage

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Aggregate error distributions, similar to Fig. \ref{fig:example_30} for the main example, but now for a collection of 20 replicate trees. For each setting (true generative, true best candidate, twin generative and twin best candidate), the resulting errors from each replicate pipeline have been merged into a single distribution.}
  \label{fig:replicate_trees}
\end{figure}

>>>>

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{
    Aggregate error distributions, similar to Fig. \ref{fig:example_30} 
    for the main example, but now for a collection of 20 replicate trees. 
    For each setting (true generative, true best candidate, twin generative 
    and twin best candidate), the resulting errors from each replicate 
    pipeline have been merged into a single distribution.
  }
  \label{fig:replicate_trees}
\end{figure}
